### 2020-04-20 final_report/methodology.tex
add (hopefully) last bit on metrics, and speedup

\Cref{tbl:metrics} provides exhaustive list and description of metrics recorded
in the experiments. For regression performance analysis, we include a selection
of absolute metrics to assess the approximation capability of surrogates, and set
practical bounds on the expected accuracy of their predictions. In addition, we also track
relative measures that are better-suited for model comparison between works as
they maintain invariance with respect to the domain and image space.

\begin{table}[h]
	\centering
	\begin{tabular}{lll}
	\toprule
	Regression performance metrics	& Mathematical formulation / description & Ideal value \\
	\midrule
	Mean absolute error (MAE)	& $\sum_{i=1}^N |y^{(i)}-\hat{y}^{(i)}|/N$ & 0
	[TBR] \\
	Standard error of regression $S$	& $\text{StdDev}_{i=1}^N\left( |y^{(i)} -
	\hat{y}^{(i)}| \right) $	 & 0 [TBR] \\
	$R^2$ ratio (coefficient of determination)	& $1-\sum_{i=1}^N \left(y^{(i)}-\hat{y}^{(i)} \right)^2 /
	\sum_{i=1}^N \left( y^{(i)}-\overline{y} \right)^2 $ & 1 [rel.] \\
	Adjusted $R^2$ ratio	& $1-(1-R^2)(N-1)/(N-P-1)$	& 1 [rel.] \\
	\midrule
	Evaluation time metrics	& {} & {} \\
	\midrule
	Mean sample training time	& $(\text{wall training time of
	$\hat{f}(x)$})/N_0$ 	& 0 [ms] \\
	Mean sample prediction time	& $(\text{wall evaluation time of
	$\hat{f}(x)$})/N$	& 0 [ms] \\
	\bottomrule
	\end{tabular}
	\caption{Metrics recorded in supervised learning experiments. In
	formulations, we work with training set of size $N_0$ and testing set of
size $N$, TBR values $y^{(i)}=f(x^{(i)})$ and $\hat{y}^{(i)}=\hat{f}(x^{(i)})$
denote images of the $i$th testing sample in the expensive model and the surrogate
respectively. Furthermore, the mean $\overline{y}=\sum_{i=1}^N y^{(i)}/N$ and $P$ is the
number of input features.}
	\label{tbl:metrics}
\end{table}

>>>>

\Cref{tbl:metrics} provides exhaustive listing and description of metrics recorded
in the experiments. For regression performance analysis, we include a selection
of absolute metrics to assess the approximation capability of surrogates, and set
practical bounds on the expected accuracy of their predictions. In addition, we also track
relative measures that are better-suited for model comparison between works as
they maintain invariance with respect to the selected domain and image space.
For analysis of evaluation time, surrogates are assessed in terms of wall time
elapsed during training and predicition. This closely models the practical use
case, in which they are trained and used as drop-in replacements for the
expensive model. Since training set sizes remain to be determined, all times are
reported per a single sample. Even though some surrogates support acceleration
by means of parallelisation, measures were taken to ensure sequential
processing of samples to achieve comparability between considered models.

\begin{table}[h]
	\centering
	\begin{tabular}{lll}
	\toprule
	Regression performance metrics	& Mathematical formulation / description & Ideal value \\
	\midrule
	Mean absolute error (MAE)	& $\sum_{i=1}^N |y^{(i)}-\hat{y}^{(i)}|/N$ & 0
	[TBR] \\
	Standard error of regression $S$	& $\text{StdDev}_{i=1}^N\left( |y^{(i)} -
	\hat{y}^{(i)}| \right) $	 & 0 [TBR] \\
	$R^2$ ratio (coefficient of determination)	& $1-\sum_{i=1}^N \left(y^{(i)}-\hat{y}^{(i)} \right)^2 /
	\sum_{i=1}^N \left( y^{(i)}-\overline{y} \right)^2 $ & 1 [rel.] \\
	Adjusted $R^2$ ratio	& $1-(1-R^2)(N-1)/(N-P-1)$	& 1 [rel.] \\
	\midrule
	Evaluation time metrics	& {} & {} \\
	\midrule
	Mean sample training time $\overline{t}_{\text{trn.}}$	& $(\text{wall training time of
	$\hat{f}(x)$})/N_0$ 	& 0 [ms] \\
	Mean sample prediction time $\overline{t}_{\text{pred.}}$	& $(\text{wall prediction time of
	$\hat{f}(x)$})/N$	& 0 [ms] \\
	Relative speedup	& $(\text{wall evaluation time of $f(x)$}) /
	(N\overline{t}_{\text{pred.}})$	&
	$\to\infty$ [rel.] \\
	\bottomrule
	\end{tabular}
	\caption{Metrics recorded in supervised learning experiments. In
	formulations, we work with training set of size $N_0$ and testing set of
size $N$, TBR values $y^{(i)}=f(x^{(i)})$ and $\hat{y}^{(i)}=\hat{f}(x^{(i)})$
denote images of the $i$th testing sample in the expensive model and the surrogate
respectively. Furthermore, the mean $\overline{y}=\sum_{i=1}^N y^{(i)}/N$ and $P$ is the
number of input features.}
	\label{tbl:metrics}
\end{table}
